Phenology and Mycorrhizae Manuscript

### 2023-01-12 manuscriptCode_phenologyAndMycorrhizae.Rmd
Prepare .Rmd to download new data.

#Single Air Temperature At Various Heights 
```{r}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"

@@

#Triple Air Temperature at Top of Canopy
```{r} 
##Need to redownload!! 
dataName="NEON_TemperatureData"
NEON_ID='DP1.00003.001'
selectColumns <- c('tempTripleMean','finalQF')
inFileName <- "TAAT_30min.csv"
varName <- 'tempTripleMean'

@@

#Precipitation
```{r}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"

@@

#NEON Phenology Observations 
```{r}
source('combineNEONdata_PhenoObs.R')
dataName="NEON_PhenologyObservations"
NEON_ID='DP1.10055.001'

@@

#Download NEON Soil Microbe Data
```{r}
dataName="NEON_SoilMicrobeComposition"
NEON_ID='DP1.10081.001'
#selectColumns <-
inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
#varName <-

@@

#Download NEON Soil Physical and Chemical Properties
```{r}
dataName <- "NEON_soilProperties"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
NEON_ID <- "DP1.10086.001"
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
#inFileNames <- c(,"sls_soilMoisture","sls_soilpH")
inFileName <- "sls_soilCoreCollection.csv"
selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
                   'soilTemp','litterDepth','sampleTopDepth','sampleBottomDepth')
dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

@@

#NEON PhenoCam Observations
```{r}
source('determinePhenoCamURLs.R')
source('downloadPhenoCamAndCalculateTransitions.R') #Still need to change to have it save it somewhere

>>>>

#Single Air Temperature At Various Heights 
```{r,eval=FALSE}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"

@@

#Triple Air Temperature at Top of Canopy
```{r,eval=FALSE} 
##Need to redownload!! 
dataName="NEON_TemperatureData"
NEON_ID='DP1.00003.001'
selectColumns <- c('tempTripleMean','finalQF')
inFileName <- "TAAT_30min.csv"
varName <- 'tempTripleMean'

@@

#Precipitation
```{r,eval=FALSE}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"

@@

#NEON Phenology Observations 
```{r,eval=FALSE}
source('combineNEONdata_PhenoObs.R')
dataName="NEON_PhenologyObservations"
NEON_ID='DP1.10055.001'

@@

#Download NEON Soil Microbe Data
```{r,eval=FALSE}
dataName="NEON_SoilMicrobeComposition"
NEON_ID='DP1.10081.001'
#selectColumns <-
inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
#varName <-

@@

#Download NEON Soil Physical and Chemical Properties
```{r,eval=FALSE}
dataName <- "NEON_soilProperties"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
NEON_ID <- "DP1.10086.001"
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
#inFileNames <- c(,"sls_soilMoisture","sls_soilpH")
inFileName <- "sls_soilCoreCollection.csv"
selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
                   'soilTemp','litterDepth','sampleTopDepth','sampleBottomDepth')
dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)

@@

#NEON PhenoCam Observations
```{r,eval=FALSE}
source('determinePhenoCamURLs.R')
source('downloadPhenoCamAndCalculateTransitions.R') #Still need to change to have it save it somewhere
